### 2011-02-10 paper/results.tex
5.2 done + minor

The results for the parameterized gaits are shown in
\figref{std_error} and \tabref{results}.  As a group, these strategies
produced results equal to or worse not significantly better than the randomly-generated
gaits, however, all methods managed to explore the space enough to
significantly improve on the previous hand coded gait in at least one
of the three runs.  No single strategy consistently outperformed the
others: for the first trial Linear Regression produced the fastest
gait at 27.58 body lengths/minute, for the second a random gait
actually won with 17.26 body lengths/minute, and for the third trial
the Nelder-Mead simplex method attained the fastest gait at 14.83 body
lengths/minute.

@@

\acmFig{std_error}{1}{Average results ($\pm $ SE) for each
  of the parameterized learning methods.  Linear regression found the
  fastest overall gait and had the highest average, followed by
  Nelder-Mead simplex. Many methods were beaten by the random
  strategy.}

>>>>

The results for the parameterized gaits are shown in
\figref{std_error} and \tabref{results}.  The best overall gait for
the parameterized methods was found by linear regression, which also
had the highest average performance. The Nelder-Mead simplex also
performed quite well on average.  The other local search methods did not
outperform random search; however, all methods did manage to explore
enough of the parameter space to significantly improve on the previous
hand-coded gait in at least one of the three runs.  No single strategy
consistently beat the others: for the first trial Linear Regression
produced the fastest gait at 27.58 body lengths/minute, for the second
a random gait actually won with 17.26 body lengths/minute, and for the
third trial the Nelder-Mead simplex method attained the fastest gait
at 14.83 body lengths/minute.

One reason the randomly-generated SineModel5 gaits were so effective
may have been due to the SineModel5's bias toward regular, symmetric
gaits.  This may have allowed the random strategy --- focusing on
exploration --- to be competitive with the more directed strategies
that exploit information from past runs.

@@

\acmFig{std_error}{1}{Average results ($\pm $ SE) for each of the
  parameterized learning methods.  Linear regression found the fastest
  overall gait and had the highest average, followed by Nelder-Mead
  simplex. Other methods did not outperform a random strategy.}
